---
title: "Subtyping latent profiles of affect in self-injurious behaviors"
author: "Madeline M. Navea"
date: "2024-10-30"
output: html_document
---
# Analytic Plan
-   Step 1. Prepare the data
-   Step 2. Estimate latent profiles of affect
-   Step 3. Examine prospective associations between profiles and both same-day and next-day self-injurious behaviors.

```{r setup}
# Load Libraries
library(tidyverse)
library(magrittr)
library(tidyLPA)
library(mclust)
library(missForest)
library(mice)
library(cowplot)
library(beepr)
library(Matrix)
#library(foreign)
#library(expss)
#library(DescTools)
#library(Rmisc)
#library(lsr)
#library(effectsize)
#library(matrixStats)
#library(knitr)
#library(patchwork)
#library(multcomp)
#library(sjstats)
#library(sjPlot)
#library(sjmisc)
#library(sjlabelled)
#library(DataCombine)
#library(modelsummary)
#library(fmsb)

# Function to convert H:M:S format to minutes
to_minutes <- function(time_str) {
  if (time_str == " ") {
    return(NA)                             # Return NA if the string is empty
  } else {
    parts <- strsplit(time_str, ":")[[1]]  # Split the string by ":"
    hours <- as.numeric(parts[1])          # Extract hours
    minutes <- as.numeric(parts[2])        # Extract minutes
    return(hours * 60 + minutes)           # Calculate total minutes
  }}
```

# Prepping data
```{r data_prep}
# Read the data frame
raw_data <- read.csv("Raw data/CompleteDay3Up.csv")

# Creating subset data frame
lpa_data <- raw_data %>% 
  dplyr::select(
    PersonID,                                                                                       # Identifier
    Male, Ethnicity, Race, Height_totalin, Weight, BMI, Age, Gen,                                   # Demographics
    SessionTime, studydays, EMA_instances, EMA_total,                                               # EMA Metadata
    Distress, Excited, Upset, Inspired, Nervous,                                                    
    Determined, Scared, Afraid, Enthusiast, Alert,                                                  
    SIB_Binge, SIB_Vomit, SIB_Laxative, SIB_Exercise, SIB_Fast, SIB_Restrict, SIB_NSSI,             # Binary engagement of SIB
    BingeMinutes, VomitMinutes, LaxMinutes, ExMinutes, FastMinutes, ResMinutes, NSSIMinutes) %>%    # SIB duration
    dplyr::rename(day_number = studydays) %>% 
    mutate_all(~ ifelse(. == -999, NA, .),
             ~ ifelse(. == "NaN", NA, .)) 
  
# Converting SIB duration from H:M:S format to minutes
lpa_data %<>%
  mutate(
    BingeMinutes_usethis = sapply(BingeMinutes, to_minutes),
    VomitMinutes_usethis = sapply(VomitMinutes, to_minutes),
    LaxMinutes_usethis = sapply(LaxMinutes, to_minutes),
    ExMinutes_usethis = sapply(ExMinutes, to_minutes),
    FastMinutes_usethis = sapply(FastMinutes, to_minutes),
    ResMinutes_usethis = sapply(ResMinutes, to_minutes),
    NSSIMinutes_usethis = sapply(NSSIMinutes, to_minutes)) %>% 
  
# Combining affect, SIB engagement, and SIB duration
    mutate(
      Affect_intensity = rowSums(
        dplyr::select(., c(Distress, Excited, Upset, Inspired, 
                           Nervous, Determined, Scared, Afraid, Enthusiast, Alert)), na.rm = TRUE),
     Excited_Enthusiast = rowMeans(cbind(Excited, Enthusiast), na.rm = TRUE),
    Scared_Afraid = rowMeans(cbind(Scared, Afraid), na.rm = TRUE),
      SIB_engagement = rowSums(
        dplyr::select(., c(SIB_Binge,SIB_Vomit,SIB_Laxative, SIB_Exercise,SIB_Fast, SIB_Restrict, SIB_NSSI)), na.rm = TRUE),
      SIB_duration = rowSums(
        dplyr::select(., c(BingeMinutes_usethis, VomitMinutes_usethis, LaxMinutes_usethis, ExMinutes_usethis, FastMinutes_usethis, ResMinutes_usethis, NSSIMinutes_usethis)),na.rm=TRUE))

# Create meta data
# Use the SessionTime variable to count off observations
# Convert SessionTime to a POSIXct object
lpa_data$SessionTime <- as.POSIXct(lpa_data$SessionTime, format = "%m/%d/%y %H:%M")
 
# Group by ID and count the number of session times
lpa_data %<>%
  arrange(PersonID, day_number, SessionTime) %>%   # Arrange data for counting
  group_by(PersonID) %>%                           # Group by ID_MOMENT and day number
  mutate(observation_number = row_number())        # Count observations within each group

# View the resulting data frame
table(lpa_data$day_number)                         # Observations look good
table(lpa_data$observation_number)                 # Number of days looks good

# Calculate maximum day and observation number for each ID_MOMENT
max_num <- lpa_data %>%
  group_by(PersonID) %>%
  summarise(day_total = max(day_number, na.rm = TRUE),
            observation_total = max(observation_number, na.rm = TRUE))

# Join day_total into profile_wide
lpa_data %<>%
  left_join(max_num, by = "PersonID")

lpa_data %<>%
  mutate(
    SIB_engagement_binary = ifelse(SIB_engagement > 0, 1, 0)) %>% 
  mutate(
    SIB_engagement_binary_lagged = lag(SIB_engagement_binary, n = 1),
    SIB_duration_lagged = lag(SIB_duration, n = 1),
    SIB_engagement_lagged = lag(SIB_engagement, n = 1))

# Create a wide-form version of the data for LPA construction
lpa_data_calculated <- lpa_data %>% 
  dplyr::select(
    PersonID, observation_number, observation_total,
    Distress, Upset, Inspired, Nervous,                                                    
    Determined, Scared, Afraid, Excited, Enthusiast, Scared_Afraid, Excited_Enthusiast, Alert, 
    SIB_engagement_binary_lagged, SIB_engagement_lagged, SIB_duration_lagged) %>% 
  unique() %>% 
   mutate_all(~ ifelse(. == "NaN", NA, .)) %>% 
  ungroup()
```
# Model 1 Outputs 
```{r}
data_imputed <- readRDS("RDS/data_imputed.rds")

LPA_model1_profile1 <- readRDS("RDS/LPA_model1_profile1.rds")
LPA_model1_profile2 <- readRDS("RDS/LPA_model1_profile2.rds")
LPA_model1_profile3 <- readRDS("RDS/LPA_model1_profile3.rds")
LPA_model1_profile4 <- readRDS("RDS/LPA_model1_profile4.rds")
LPA_model1_profile5 <- readRDS("RDS/LPA_model1_profile5.rds")
LPA_model1_profile6 <- readRDS("RDS/LPA_model1_profile6.rds")

LPA_model1_profile1_df <- readRDS("RDS/LPA_model1_profile1_df.rds")
LPA_model1_profile2_df <- readRDS("RDS/LPA_model1_profile2_df.rds")
LPA_model1_profile3_df <- readRDS("RDS/LPA_model1_profile3_df.rds")
LPA_model1_profile4_df <- readRDS("RDS/LPA_model1_profile4_df.rds")
LPA_model1_profile5_df <- readRDS("RDS/LPA_model1_profile5_df.rds")
LPA_model1_profile6_df <- readRDS("RDS/LPA_model1_profile6_df.rds")

plot_long1_1 <- readRDS("RDS/plot_long1_1.rds")
plot_long1_2 <- readRDS("RDS/plot_long1_2.rds")
plot_long1_3 <- readRDS("RDS/plot_long1_3.rds")
plot_long1_4 <- readRDS("RDS/plot_long1_4.rds")
plot_long1_5 <- readRDS("RDS/plot_long1_5.rds")
plot_long1_6 <- readRDS("RDS/plot_long1_6.rds")

plot_model1_profile1 <- readRDS("RDS/plot_model1_profile1.rds")
plot_model1_profile2 <- readRDS("RDS/plot_model1_profile2.rds")
plot_model1_profile3 <- readRDS("RDS/plot_model1_profile3.rds")
plot_model1_profile4 <- readRDS("RDS/plot_model1_profile4.rds")
plot_model1_profile5 <- readRDS("RDS/plot_model1_profile5.rds")
plot_model1_profile6 <- readRDS("RDS/plot_model1_profile6.rds")
```

# Model 1 Plot Outputs 
```{r}
plot_1_1 <- readRDS("RDS/plot_1_1.rds")
plot_1_2 <- readRDS("RDS/plot_1_2.rds")
plot_1_3 <- readRDS("RDS/plot_1_3.rds")
plot_1_4 <- readRDS("RDS/plot_1_4.rds")
plot_1_5 <- readRDS("RDS/plot_1_5.rds")
plot_1_6 <- readRDS("RDS/plot_1_6.rds")
plot_1_7 <- readRDS("RDS/plot_1_7.rds")
plot_1_8 <- readRDS("RDS/plot_1_8.rds")
plot_1_9 <- readRDS("RDS/plot_1_9.rds")
plot_1_10 <- readRDS("RDS/plot_1_10.rds")
plot_1_11 <- readRDS("RDS/plot_1_11.rds")

plot_1_1
plot_1_2
plot_1_3
plot_1_4
plot_1_5
plot_1_6
plot_1_7
plot_1_8
plot_1_9
plot_1_10
plot_1_11

ggsave("Outputs/Model 1.jpeg", plot = plot_grid(
  plot_1_1,
  plot_1_2,
  plot_1_3,
  plot_1_4,
  plot_1_5,
  plot_1_6,
  plot_1_7,
  plot_1_8,
  plot_1_9,
  plot_1_10,
  plot_1_11, ncol = 5, align = "h", rel_widths = c(1.2, 1.2, 1.2, 1.2, 1.2)), width = 50, height = 20, limitsize = F)
```
################################################################################################################################
##################################### COMMENTED CODE HAS BEEN SAVED IN RDS FILES ###############################################
################################################################################################################################
# Getting effect estimates for best fit solution:
```{r message=FALSE, warning=FALSE}
# set.seed(123)
# LPA <- lpa_data_calculated[1:6600, ] %>%
#   dplyr::select(Distress, Excited_Enthusiast, Upset, Inspired, Nervous,                                           
#     Determined, Scared_Afraid, Alert) %>% 
#     estimate_profiles(1:6, 
#                     variances = c("varying", "varying", "equal", "equal"),
#                     covariances = c("zero", "varying", "zero", "equal")) %>%
#   compare_solutions(statistics = c("AIC", "BIC", "SABIC", "Entropy", "LogLik"))
# print(LPA)
# beep()
# saveRDS(LPA, file = "RDS/LPA.rds")
# LPA <- readRDS("RDS/LPA.rds")

# TidyLPA allows for 4 models (Model 1, 2, 3, and 6)
# Mplus allows for an additional 2 models (Model 4 and 5)
# Equal variances and covariances fixed to 0 (Model 1)
# Varying variances and covariances fixed to 0 (Model 2)
# Equal variances and equal covariances (Model 3)
# Varying variances and equal covariances (Model 4)
# Equal variances and varying covariances (Model 5)
# Varying variances and varying covariances (Model 6)
```
# Impute data
```{r}
# set.seed(123)
# lpa_data_imputed <- lpa_data_calculated[1:6600, ] %>%
#   dplyr::select(Distress, Upset, Inspired, Nervous,                                                  
#                 Determined, Scared_Afraid, Excited_Enthusiast, Alert)
# imputed_data <- mice(lpa_data_imputed, method = "rf", m = 1) #use random forest imputation
# data_imputed <- complete(imputed_data, 1)
# 
# # Checking if there are any NAs
# any(is.na(data_imputed))
# saveRDS(data_imputed, file = "RDS/data_imputed.rds")
```
# Estimate Model 1 Profile 5
```{r}
# # estimate profiles
# set.seed(123)
# LPA_model1_profile5 <- Mclust(data_imputed, G = 5, modelNames = "EEI") 
# LPA_model1_profile5_df <- data.frame(
#   ID = 1:length(LPA_model1_profile5$classification),
#   Class = LPA_model1_profile5$classification)
# classification1_5 <- LPA_model1_profile5$classification
# LPA_model1_profile5_df <- cbind(
#   lpa_data_calculated,                      
#   Class = classification1_5)
```
################################################################################################################################
##################################### COMMENTED CODE HAS BEEN SAVED IN RDS FILES ###############################################
################################################################################################################################

#Prepare data for plotting
```{r}
# pivoting longer
plot_long1_5 <- LPA_model1_profile5_df %>%
  dplyr::select(Class, 
                Distress, Upset, Inspired, Nervous,                                                  
    Determined, Scared_Afraid, Excited_Enthusiast, Alert) %>%  
  pivot_longer(cols = c(
    Distress, Upset, Inspired, Nervous,                                                    
    Determined, Scared_Afraid, Excited_Enthusiast,, Alert), 
               names_to = "Affect",
               values_to = "Affect_score")

# creating mean, sd, etc.
plot_model1_profile5 <- plot_long1_5 %>%
  dplyr::group_by(Class, Affect) %>%
  dplyr::summarise(mean_score = mean(Affect_score, na.rm = TRUE),
                   sd_score = sd(Affect_score, na.rm = TRUE),
                   n = n(), .groups = "drop") %>%
  mutate(se_score = sd_score / sqrt(n)) %>% 
  ungroup()
plot_model1_profile5$Class <- factor(plot_model1_profile5$Class)

plot_model1_profile5$Affect <- factor(plot_model1_profile5$Affect, 
         levels = c("Distress", "Upset", "Nervous", "Scared_Afraid", 
                    "Inspired", "Determined", "Alert", "Excited_Enthusiast"))
```

# Posterior probabilities
```{r message=FALSE, warning=FALSE}
profileDf <- function(model, data, solution_number) {
  posterior_probs <- as.data.frame(model$z)
  colnames(posterior_probs) <- paste0("Class_", 1:ncol(posterior_probs))
  
  profile_df <- data %>%
    dplyr::mutate(
      Class = model$classification,
      posterior_prob = apply(posterior_probs, 1, max),
      Assigned_Class = apply(posterior_probs, 1, which.max)
    ) %>%
    dplyr::select(Class, posterior_prob, Assigned_Class) %>%
    dplyr::mutate(Solution = solution_number)
  
  return(profile_df)
}

# Generate profiles for each solution
profile1 <- profileDf(LPA_model1_profile1, data_imputed, 1)
profile2 <- profileDf(LPA_model1_profile2, data_imputed, 2)
profile3 <- profileDf(LPA_model1_profile3, data_imputed, 3)
profile4 <- profileDf(LPA_model1_profile4, data_imputed, 4)
profile5 <- profileDf(LPA_model1_profile5, data_imputed, 5)
profile6 <- profileDf(LPA_model1_profile6, data_imputed, 6)


posteriors1 <- profile1 %>% group_by(Class) %>%
  summarize(
    mean_posprob = mean(posterior_prob),
    prop_over80 = mean(posterior_prob > 0.8)) %>%
  mutate(Solution = 1)

#create for each
posteriors2 <- profile2 %>% group_by(Class) %>%
  summarize(mean_posprob = mean(posterior_prob), prop_over80 = mean(posterior_prob > 0.8)) %>% mutate(Solution = 2)
posteriors3 <- profile3 %>% group_by(Class) %>% summarize(mean_posprob = mean(posterior_prob), prop_over80 = mean(posterior_prob > 0.8)) %>% mutate(Solution = 3)
posteriors4 <- profile4 %>% group_by(Class) %>% summarize(mean_posprob = mean(posterior_prob), prop_over80 = mean(posterior_prob > 0.8)) %>% mutate(Solution = 4)
posteriors5 <- profile5 %>% group_by(Class) %>% summarize(mean_posprob = mean(posterior_prob), prop_over80 = mean(posterior_prob > 0.8)) %>% mutate(Solution = 5)
posteriors6 <- profile6 %>% group_by(Class) %>% summarize(mean_posprob = mean(posterior_prob), prop_over80 = mean(posterior_prob > 0.8)) %>% mutate(Solution = 6)

# Bind all together
posterior_summary <- bind_rows(posteriors1, posteriors2, posteriors3, posteriors4, posteriors5, posteriors6)
write.csv(posterior_summary, "Outputs/Table1_Posteriors1.csv", row.names = FALSE)
```

#plot affect profiles
```{r}
plot_1_5 <- ggplot(plot_model1_profile5, aes(x = Affect, y = mean_score, group = Class, 
                                              color = Class, shape = Class, fill = Class)) +
  geom_point(size = 3, stroke = 1) +
  geom_line(size = 1.25) +
  # geom_errorbar(aes(ymin = mean_score - se_score, ymax = mean_score + se_score), width = 2) +
  scale_color_manual(values = c("1" = "#1D6E9A", "2" = "#E4ACDF", "3" = "#221D23", "4" = "#FE5F55",
                                 "5"= "#A36678")) +
  scale_fill_manual(values = c("1" = "#1D6E9A", "2" = "#E4ACDF", "3" = "#221D23", "4" = "#FE5F55",
                                "5" = "#A36678")) +
  scale_shape_manual(values = c("1" = 21, "2" = 22, "3" = 23, "4" = 24, "5" = 25)) +
  scale_x_discrete(labels = c("Scared_Afraid" = "Scared/Afraid", 
                              "Excited_Enthusiast" = "Excited/Enthusiastic")) +
  labs(title = "Affective States by Profile",
       x = " ",
       y = "Score",
       color = "Class",
       shape = "Class",
       fill = "Class",
       linetype = "Class") +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right")

ggsave("Outputs/Affect_classes.jpeg", width = 7, height = 6)
```

# Plot Class associations with SIBs
# Frequency
```{r}
# Prepare data to plot class associations with SIBs

# create frequency counts for each type of sib
sib_totals <- lpa_data %>%
  group_by(PersonID, observation_number) %>%
  summarise(
    SIB_Binge = sum(SIB_Binge, na.rm = TRUE),
    SIB_Vomit = sum(SIB_Vomit, na.rm = TRUE),
    SIB_Laxative = sum(SIB_Laxative, na.rm = TRUE),
    SIB_Exercise = sum(SIB_Exercise, na.rm = TRUE),
    SIB_Fast = sum(SIB_Fast, na.rm = TRUE),
    SIB_Restrict = sum(SIB_Restrict, na.rm = TRUE),
    SIB_NSSI = sum(SIB_NSSI, na.rm = TRUE),
    Total_SIBs = sum(SIB_Binge, SIB_Vomit, SIB_Laxative, SIB_Exercise, SIB_Fast, SIB_Restrict, SIB_NSSI, na.rm = TRUE)) %>% 
  mutate(
    tracking = paste0(PersonID, "_", observation_number)) #track the type of sib for each person (merge by this later)

df_freq_plot <- LPA_model1_profile5_df %>%
  dplyr::select(PersonID, Class, observation_number) %>% 
  mutate(
    tracking = paste0(PersonID, "_", observation_number)) #track the type of sib for each person (merge by this later)

freq_plot <- merge(df_freq_plot, sib_totals, by = "tracking") #merge by the tracking column
table(freq_plot$Class)

#group by class and create class sums for each sib type, along with the total SIB count
test1 <- freq_plot %>%
  dplyr::group_by(Class) %>%
  dplyr::summarise(
    Total_SIB_Binge = sum(SIB_Binge, na.rm = TRUE),
    Total_SIB_Vomit = sum(SIB_Vomit, na.rm = TRUE),
    Total_SIB_Laxative = sum(SIB_Laxative, na.rm = TRUE),
    Total_SIB_Exercise = sum(SIB_Exercise, na.rm = TRUE),
    Total_SIB_Fast = sum(SIB_Fast, na.rm = TRUE),
    Total_SIB_Restrict = sum(SIB_Restrict, na.rm = TRUE),
    Total_SIB_NSSI = sum(SIB_NSSI, na.rm = TRUE),
    Total_SIBs = sum(Total_SIB_Binge, Total_SIB_Vomit, Total_SIB_Laxative, 
                    Total_SIB_Exercise, Total_SIB_Fast, Total_SIB_Restrict, Total_SIB_NSSI, 
                    na.rm = TRUE))
# pivot df longer
freq_plot %<>%
  dplyr::select(Class, SIB_Binge, SIB_Vomit, SIB_Laxative, SIB_Exercise, SIB_Fast, SIB_Restrict, SIB_NSSI) %>%  
  pivot_longer(cols = c(SIB_Binge, SIB_Vomit, SIB_Laxative, SIB_Exercise, SIB_Fast, SIB_Restrict, SIB_NSSI), 
               names_to = "SIBs",
               values_to = "SIB_score") %>% 
  #rename them for visuals
  mutate(
    SIBs = case_when(
      SIBs == "SIB_Binge" ~ "Binge",
      SIBs == "SIB_Vomit" ~ "Vomit",
      SIBs == "SIB_Laxative" ~ "Laxative",
      SIBs == "SIB_Exercise" ~ "Exercise",
      SIBs == "SIB_Fast" ~ "Fast",
      SIBs == "SIB_Restrict" ~ "Restrict",
      SIBs == "SIB_NSSI" ~ "NSSI",
      TRUE ~ SIBs)) %>%
  group_by(Class, SIBs) %>%
  summarise(total_SIB_score = sum(SIB_score, na.rm = TRUE)) %>%
  ungroup()

freq_plot$total_SIB_score <- as.numeric(freq_plot$total_SIB_score)
```

#Plot for Class Associations with SIBs
```{r}
ggplot(freq_plot, aes(x = SIBs, y = total_SIB_score, fill = factor(Class))) +
  geom_col(position = "dodge") + 
  scale_fill_manual(values = c("1" = "#1D6E9A", "2" = "#E4ACDF", "3" = "#221D23", 
                               "4" = "#FE5F55", "5"= "#A36678")) +
  scale_y_continuous(limits = c(0, 60)) +
  labs(title = "SIBs by Affective Profile",
       x = " ",
       y = "Total SIB Counts",
       fill = "Class") +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("Outputs/LPA_by_SIB_freq.jpg", dpi = 2000, width = 7, height = 6)
```

# Extra plot depicting the Mean
```{r}
sib_totals <- lpa_data %>%
  group_by(PersonID) %>%
  summarise(
    SIB_Binge = sum(SIB_Binge, na.rm = TRUE),
    SIB_Vomit = sum(SIB_Vomit, na.rm = TRUE),
    SIB_Laxative = sum(SIB_Laxative, na.rm = TRUE),
    SIB_Exercise = sum(SIB_Exercise, na.rm = TRUE),
    SIB_Fast = sum(SIB_Fast, na.rm = TRUE),
    SIB_Restrict = sum(SIB_Restrict, na.rm = TRUE),
    SIB_NSSI = sum(SIB_NSSI, na.rm = TRUE),
    Total_SIBs = sum(SIB_Binge, SIB_Vomit, SIB_Laxative, SIB_Exercise, SIB_Fast, SIB_Restrict, SIB_NSSI, na.rm = TRUE))

df_plot <- LPA_model1_profile5_df %>%
  dplyr::select(PersonID, Class) %>%
  left_join(sib_totals %>%
              dplyr::select(PersonID, SIB_Binge, SIB_Vomit, SIB_Laxative, 
                            SIB_Exercise, SIB_Fast, SIB_Restrict, SIB_NSSI, Total_SIBs),
            by = "PersonID")
df_plot$Class <- as.factor(df_plot$Class)
table(df_plot$Class)

df_plot %<>%
  dplyr::select(Class, SIB_Binge, SIB_Vomit, SIB_Laxative, SIB_Exercise, SIB_Fast, SIB_Restrict, SIB_NSSI) %>%  
  pivot_longer(cols = c(SIB_Binge, SIB_Vomit, SIB_Laxative, SIB_Exercise, SIB_Fast, SIB_Restrict, SIB_NSSI), 
               names_to = "SIBs",
               values_to = "SIB_score") %>% 
  mutate(
    SIBs = case_when(
      SIBs == "SIB_Binge" ~ "Binge",
      SIBs == "SIB_Vomit" ~ "Vomit",
      SIBs == "SIB_Laxative" ~ "Laxative",
      SIBs == "SIB_Exercise" ~ "Exercise",
      SIBs == "SIB_Fast" ~ "Fast",
      SIBs == "SIB_Restrict" ~ "Restrict",
      SIBs == "SIB_NSSI" ~ "NSSI",
      TRUE ~ SIBs)) %>%
  group_by(Class, SIBs) %>%
  dplyr::summarise(mean_score = mean(SIB_score, na.rm = TRUE),
            sd_score = sd(SIB_score, na.rm = TRUE),
            n = n()) %>%
  mutate(se_score = sd_score / sqrt(n)) %>% 
  ungroup()

ggplot(df_plot, aes(x = SIBs, y = mean_score, group = Class, color = Class, shape = Class, fill = Class)) +
  geom_point(size = 4) + 
  geom_line(size = 1.25) +
  #geom_jitter(aes(color = Class, shape = Class), width = 0.15, size = 2.25, alpha = 0.65) +
  scale_color_manual(values = c("1" = "#1D6E9A", "2" = "#E4ACDF", "3" = "#221D23", "4" = "#FE5F55",
                                 "5"= "#A36678")) +
  scale_fill_manual(values = c("1" = "#1D6E9A", "2" = "#E4ACDF", "3" = "#221D23", "4" = "#FE5F55",
                                "5" = "#A36678")) +
  scale_shape_manual(values = c("1" = 21, "2" = 22, "3" = 23, "4" = 24, "5" = 25)) + 
  labs(title = "SIBs by Affective Class",
       x = " ",
       y = "Score",
       color = "Class",
       shape = "Class") +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right") 

ggsave("Outputs/LPA_by_SIBs.jpg", dpi = 2000, width = 8, height = 6)
```
